An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-14 VLDB2026/main.tex

>>>>

%	 修改此处
	ACORN performs similarly on both large and small range queries, but its overall performance is worse than the other methods.

	For third-party libraries and databases, Figure~\ref{fig:exp_8_2} shows that Faiss performs well in range filtering and even outperforms some specialized range query algorithms in certain cases. Faiss performs better in small-range filtering scenarios because it searches over the filtered vectors. With a smaller range, fewer points remain after filtering, resulting in lower computational cost. In addition, the performance of Faiss is influenced by data dimensionality; it tends to work better on low-dimensional datasets.

	Vector databases also show relatively poor performance on range queries. Among them, Milvus performs better than the others, even surpassing ACORN under high recall settings. PASE performs poorly on small-range queries, with recall lower than 0.1, so it does not appear in Figure~\ref{fig:exp_8_2}. VPASE also performs better on large-range queries, but compared to PASE, its performance on small ranges is significantly better, achieving higher recall despite very low QPS.
